---
title: "Fitness ~ Expression Regression"
author: "Rachel Wright"
date: "6/30/2021"
output: pdf_document
---

Fitness ~ expression regressions per treatment

Load expression and trait data

```{r}
library(tidyverse)
load("trait_data_good_names.Rdata")
head(datTraits)
```

```{r}
vsdpvals <- read.csv("29june21_WaldtoCont_VSDandPVALS.csv")
vsdpvals[1:2,c(1:5,297:307)]
```

Calculate survival rates per treatment

```{r}
surv_rates <- datTraits %>% group_by(treat) %>% summarize(meanSurv = mean(fracSurv))
surv_rates
```

Set p-value cutoff

```{r}
alpha <- 0.1
```

# Vibrio treatment
Calculate normalized survival rates per treatment for samples in those treatments


```{r}
bac_samples <- datTraits %>% filter(treat=="b") %>% select(sampleID, fracSurv) %>%
  mutate(normSurv = fracSurv/0.9)
hist(bac_samples$fracSurv)
hist(bac_samples$normSurv)
```

Up-regulated genes

```{r Up-regulated genes}
bac_expr_up <- vsdpvals %>% filter(padj.b<alpha & LFC.b>0) %>% column_to_rownames("X") %>% 
  select_if(names(.) %in% bac_samples$sampleID) %>% 
  t() %>%
  as.data.frame() %>%
  rownames_to_column("sampleID") %>%
  pivot_longer(cols = starts_with("Amillepora"), names_to = "gene", values_to = "expr") %>%
  group_by(gene) %>%
  mutate(z_score = (expr-mean(expr))/sd(expr)) %>%
  ungroup()
bac_expr_up[1:3,1:3]
```

Make data frame with expression data and survival

```{r}
bac_up_expr_surv <- merge(bac_samples, bac_expr_up, by="sampleID")
head(bac_up_expr_surv)
```

Linear model and plot

```{r}
lmBacUp <- summary(lm(normSurv~z_score,data=bac_up_expr_surv))
lmBacUp

plot_up_bac <- ggplot(bac_up_expr_surv, aes(x=z_score, y=normSurv)) +
  # geom_point() +
  geom_smooth(method=lm , color="red", fill="grey", se=TRUE) +
  xlab("Z score")+
  ylab("Normalized Survival")+
  ggtitle(paste("Upregulated in Vibrio p=",round(lmBacUp$coefficients[8],3),sep=""))+
  theme_classic()
plot_up_bac
```

Down-regulated genes

```{r Down-regulated genes}
bac_expr_down <- vsdpvals %>% filter(padj.b<alpha & LFC.b<0) %>% column_to_rownames("X") %>% 
  select_if(names(.) %in% bac_samples$sampleID) %>% 
  t() %>%
  as.data.frame() %>%
  rownames_to_column("sampleID") %>%
  pivot_longer(cols = starts_with("Amillepora"), names_to = "gene", values_to = "expr") %>%
  group_by(gene) %>%
  mutate(z_score = (expr-mean(expr))/sd(expr)) %>%
  ungroup()
bac_expr_down[1:3,1:3]
```

Make data frame with expression data and survival

```{r}
bac_down_expr_surv <- merge(bac_samples, bac_expr_down, by="sampleID")
head(bac_down_expr_surv)
```

Linear model and plot

```{r}
lmBacDown <- summary(lm(normSurv~z_score,data=bac_down_expr_surv))
lmBacDown

plot_down_bac <- ggplot(bac_down_expr_surv, aes(x=z_score, y=normSurv)) +
  # geom_point() +
  geom_smooth(method=lm , color="red", fill="grey", se=TRUE) +
  xlab("Z score")+
  ylab("Normalized Survival")+
  ggtitle(paste("Downregulated in Vibrio p=",round(lmBacDown$coefficients[8],3),sep=""))+
  theme_classic()
plot_down_bac
```


# Heat treatment

```{r}
heat_samples <- datTraits %>% filter(treat=="h") %>% select(sampleID, fracSurv) %>%
  mutate(normSurv = fracSurv/0.8724138)
hist(heat_samples$fracSurv)
hist(heat_samples$normSurv)
```

Filter expression data per treatment and genes DE in that treatment

Up-regulated genes

```{r Up-regulated genes}
heat_expr_up <- vsdpvals %>% filter(padj.h<alpha & LFC.h>0) %>% column_to_rownames("X") %>% 
  select_if(names(.) %in% heat_samples$sampleID) %>% 
  t() %>%
  as.data.frame() %>%
  rownames_to_column("sampleID") %>%
  pivot_longer(cols = starts_with("Amillepora"), names_to = "gene", values_to = "expr") %>%
  group_by(gene) %>%
  mutate(z_score = (expr-mean(expr))/sd(expr)) %>%
  ungroup()
heat_expr_up[1:3,1:3]
```

Make data frame with expression data and survival

```{r}
heat_up_expr_surv <- merge(heat_samples, heat_expr_up, by="sampleID")
head(heat_up_expr_surv)
```

Linear model and plot

```{r}
lmHeatUp <- summary(lm(normSurv~z_score,data=heat_up_expr_surv))
lmHeatUp

plot_up_heat <- ggplot(heat_up_expr_surv, aes(x=z_score, y=normSurv)) +
  # geom_point() +
  geom_smooth(method=lm , color="red", fill="grey", se=TRUE) +
  xlab("Z score")+
  ylab("Normalized Survival")+
  ggtitle(paste("Upregulated in 30째C p=",round(lmHeatUp$coefficients[8],3),sep=""))+
  theme_classic()
plot_up_heat
```

Down-regulated genes

```{r Down-regulated genes}
heat_expr_down <- vsdpvals %>% filter(padj.h<alpha & LFC.h<0) %>% column_to_rownames("X") %>% 
  select_if(names(.) %in% heat_samples$sampleID) %>% 
  t() %>%
  as.data.frame() %>%
  rownames_to_column("sampleID") %>%
  pivot_longer(cols = starts_with("Amillepora"), names_to = "gene", values_to = "expr") %>%
  group_by(gene) %>%
  mutate(z_score = (expr-mean(expr))/sd(expr)) %>%
  ungroup()
heat_expr_down[1:3,1:3]
```

Make data frame with expression data and survival

```{r}
heat_down_expr_surv <- merge(heat_samples, heat_expr_down, by="sampleID")
head(heat_down_expr_surv)
```

Linear model and plot

```{r}
lmHeatDown <- summary(lm(normSurv~z_score,data=heat_down_expr_surv))
lmHeatDown

plot_down_heat <- ggplot(heat_down_expr_surv, aes(x=z_score, y=normSurv)) +
  # geom_point() +
  geom_smooth(method=lm , color="red", fill="grey", se=TRUE) +
  xlab("Z score")+
  ylab("Normalized Survival")+
  ggtitle(paste("Downregulated in 30째C p=",round(lmHeatDown$coefficients[8],3),sep=""))+
  theme_classic()
plot_down_heat
```


# pCO2 treatment

```{r}
pco_samples <- datTraits %>% filter(treat=="p") %>% select(sampleID, fracSurv) %>%
  mutate(normSurv = fracSurv/0.8405455)
hist(pco_samples$fracSurv)
hist(pco_samples$normSurv)
```

Filter expression data per treatment and genes DE in that treatment

Up-regulated genes

```{r Up-regulated genes}
pco_expr_up <- vsdpvals %>% filter(padj.p<alpha & LFC.p>0) %>% column_to_rownames("X") %>% 
  select_if(names(.) %in% pco_samples$sampleID) %>% 
  t() %>%
  as.data.frame() %>%
  rownames_to_column("sampleID") %>%
  pivot_longer(cols = starts_with("Amillepora"), names_to = "gene", values_to = "expr") %>%
  group_by(gene) %>%
  mutate(z_score = (expr-mean(expr))/sd(expr)) %>%
  ungroup()
pco_expr_up[1:3,1:3]
```

Make data frame with expression data and survival

```{r}
pco_up_expr_surv <- merge(pco_samples, pco_expr_up, by="sampleID")
head(pco_up_expr_surv)
```

Linear model and plot

```{r}
lmPCOUp <- summary(lm(normSurv~z_score,data=pco_up_expr_surv))
lmPCOUp

plot_up_pco <- ggplot(pco_up_expr_surv, aes(x=z_score, y=normSurv)) +
  # geom_point() +
  geom_smooth(method=lm , color="red", fill="grey", se=TRUE) +
  xlab("Z score")+
  ylab("Normalized Survival")+
  ggtitle(paste("Upregulated in pCO2 p=",round(lmPCOUp$coefficients[8],3),sep=""))+
  theme_classic()
plot_up_pco
```

Down-regulated genes

```{r Down-regulated genes}
pco_expr_down <- vsdpvals %>% filter(padj.p<alpha & LFC.p<0) %>% column_to_rownames("X") %>% 
  select_if(names(.) %in% pco_samples$sampleID) %>% 
  t() %>%
  as.data.frame() %>%
  rownames_to_column("sampleID") %>%
  pivot_longer(cols = starts_with("Amillepora"), names_to = "gene", values_to = "expr") %>%
  group_by(gene) %>%
  mutate(z_score = (expr-mean(expr))/sd(expr)) %>%
  ungroup()
pco_expr_down[1:3,1:3]
```

Make data frame with expression data and survival

```{r}
pco_down_expr_surv <- merge(pco_samples, pco_expr_down, by="sampleID")
head(pco_down_expr_surv)
```

Linear model and plot

```{r}
lmPCODown <- summary(lm(normSurv~z_score,data=pco_down_expr_surv))
lmPCODown

plot_down_pco <- ggplot(pco_down_expr_surv, aes(x=z_score, y=normSurv)) +
  # geom_point() +
  geom_smooth(method=lm , color="red", fill="grey", se=TRUE) +
  xlab("Z score")+
  ylab("Normalized Survival")+
  ggtitle(paste("Downregulated in pCO2 p=",round(lmPCODown$coefficients[8],3),sep=""))+
  theme_classic()
plot_down_pco
```

# Combined treatment

```{r}
combined_samples <- datTraits %>% filter(treat=="a") %>% select(sampleID, fracSurv) %>%
  mutate(normSurv = fracSurv/0.8891228)
hist(combined_samples$fracSurv)
hist(combined_samples$normSurv)
```

Filter expression data per treatment and genes DE in that treatment

Up-regulated genes

```{r Up-regulated genes}
comb_expr_up <- vsdpvals %>% filter(padj.a<alpha & LFC.a>0) %>% column_to_rownames("X") %>% 
  select_if(names(.) %in% combined_samples$sampleID) %>% 
  t() %>%
  as.data.frame() %>%
  rownames_to_column("sampleID") %>%
  pivot_longer(cols = starts_with("Amillepora"), names_to = "gene", values_to = "expr") %>%
  group_by(gene) %>%
  mutate(z_score = (expr-mean(expr))/sd(expr)) %>%
  ungroup()
comb_expr_up[1:3,1:3]
```

Make data frame with expression data and survival

```{r}
combined_up_expr_surv <- merge(combined_samples, comb_expr_up, by="sampleID")
head(combined_up_expr_surv)
```

Linear model and plot

```{r}
lmCombUp <- summary(lm(normSurv~z_score,data=combined_up_expr_surv))
lmCombUp

plot_up_comb <- ggplot(combined_up_expr_surv, aes(x=z_score, y=normSurv)) +
  # geom_point() +
  geom_smooth(method=lm , color="red", fill="grey", se=TRUE) +
  xlab("Z score")+
  ylab("Normalized Survival")+
  ggtitle(paste("Upregulated in Combined p=",round(lmCombUp$coefficients[8],3),sep=""))+
  theme_classic()
plot_up_comb
```

Down-regulated genes

```{r Down-regulated genes}
comb_expr_down <- vsdpvals %>% filter(padj.a<alpha & LFC.a<0) %>% column_to_rownames("X") %>% 
  select_if(names(.) %in% combined_samples$sampleID) %>% 
  t() %>%
  as.data.frame() %>%
  rownames_to_column("sampleID") %>%
  pivot_longer(cols = starts_with("Amillepora"), names_to = "gene", values_to = "expr") %>%
  group_by(gene) %>%
  mutate(z_score = (expr-mean(expr))/sd(expr)) %>%
  ungroup()
comb_expr_down[1:3,1:3]
```

Make data frame with expression data and survival

```{r}
comb_down_expr_surv <- merge(combined_samples, comb_expr_down, by="sampleID")
head(comb_down_expr_surv)
```

Linear model and plot

```{r}
lmCombDown <- summary(lm(normSurv~z_score,data=comb_down_expr_surv))
lmCombDown

plot_down_comb <- ggplot(comb_down_expr_surv, aes(x=z_score, y=normSurv)) +
  # geom_point() +
  geom_smooth(method=lm , color="red", fill="grey", se=TRUE) +
  xlab("Z score")+
  ylab("Normalized Survival")+
  ggtitle(paste("Downregulated in Combined p=",round(lmCombDown$coefficients[8],3),sep=""))+
  theme_classic()
plot_down_comb
```

# Save all plots

```{r}
# pdf(file="fig_allCorrelations.pdf", height=10,width=10)
gridExtra::grid.arrange(
  plot_up_bac,plot_down_bac,
  plot_up_heat,plot_down_heat,
  plot_up_pco, plot_down_pco,
  plot_up_comb, plot_down_comb,
  ncol=2
)
# dev.off()
```

How many genes in each?
```{r}
n_genes <- data.frame("bac_up"= bac_expr_up %>% summarize("bac_up"=n_distinct(gene)),
           "bac_down"=bac_expr_down %>% summarize("bac_down"=n_distinct(gene)),
           "heat_up"=heat_expr_up %>% summarize("heat_up"=n_distinct(gene)),
           "heat_down"=heat_expr_down %>% summarize("heat_down"=n_distinct(gene)),
           "pco_up"=pco_expr_up %>% summarize("pco_up"=n_distinct(gene)),
           "pco_down"=pco_expr_down %>% summarize("pco_down"=n_distinct(gene)),
           "comb_up"=comb_expr_up %>% summarize("comb_up"=n_distinct(gene)),
           "comb_down"=comb_expr_down %>% summarize("comb_down"=n_distinct(gene)))
n_genes
```


# Regress bleaching score with gene expression response in heat treatment

# Heat treatment

```{r}
datTraits %>% group_by(treat) %>% summarize(mean(color.log)) # the color is an INCREASE in color

heat_samples_color <- datTraits %>% filter(treat=="h") %>% select(sampleID, color.log) %>%
  mutate(normColor = color.log/1.747530)
hist(heat_samples_color$color.log)
hist(heat_samples_color$normColor)
```

Filter expression data per treatment and genes DE in that treatment

Up-regulated genes

```{r}
heat_up_expr_color <- merge(heat_samples_color, heat_expr_up, by="sampleID")
head(heat_up_expr_color)
```

Linear model and plot

```{r}
lmHeatUpCol <- summary(lm(normColor~z_score,data=heat_up_expr_color))
lmHeatUp

plot_up_heat_col <- ggplot(heat_up_expr_color, aes(x=z_score, y=normColor)) +
  # geom_point() +
  geom_smooth(method=lm , color="red", fill="grey", se=TRUE) +
  xlab("Z score")+
  ylab("Normalized Color Increase")+
  ggtitle(paste("Upregulated in 30째C p=",round(lmHeatUp$coefficients[8],3),sep=""))+
  theme_classic()
plot_up_heat_col
```

Down-regulated genes

```{r}
heat_down_expr_color <- merge(heat_samples_color, heat_expr_down, by="sampleID")
head(heat_down_expr_color)
```

Linear model and plot

```{r}
lmHeatDownCol <- summary(lm(normColor~z_score,data=heat_down_expr_color))
lmHeatDownCol

plot_down_heat_col <- ggplot(heat_down_expr_color, aes(x=z_score, y=normColor)) +
  # geom_point() +
  geom_smooth(method=lm , color="red", fill="grey", se=TRUE) +
  xlab("Z score")+
  ylab("Normalized Color Increase")+
  ggtitle(paste("Downregulated in 30째C p=",round(lmHeatUp$coefficients[8],3),sep=""))+
  theme_classic()
plot_down_heat_col
```

```{r}
pdf(file="fig_heatCorrelationsColor.pdf", height=4,width=10)
gridExtra::grid.arrange(
  plot_up_heat_col, plot_down_heat_col,
  ncol=2
)
dev.off()
```






















# Selection Coefficients
based on adaptive gene expression PLOSGenetics paper

Format vsd for expression values only

```{r format vsd}
vsd <- vsdpvals %>% column_to_rownames("X") %>% 
  select_if(names(.) %in% datTraits$sampleID)
# make sure sample names match between expression data file (vsd) and fitness data file (datTraits)
table(names(vsd) %in% datTraits$sampleID)
table(names(vsd)==datTraits$sampleID)
```

Separate expression for each treatment

```{r}
sam_control <- datTraits$sampleID[datTraits$treat=="c"]
sam_bac <- datTraits$sampleID[datTraits$treat=="b"]
sam_heat <- datTraits$sampleID[datTraits$treat=="h"]
sam_pco <- datTraits$sampleID[datTraits$treat=="p"]
sam_comb <- datTraits$sampleID[datTraits$treat=="a"]

vsd.control <- vsd %>% select_if(names(.) %in% sam_control)
vsd.bac <- vsd %>% select_if(names(.) %in% sam_bac)
vsd.heat <- vsd %>% select_if(names(.) %in% sam_heat)
vsd.pco <- vsd %>% select_if(names(.) %in% sam_pco)
vsd.comb <- vsd %>% select_if(names(.) %in% sam_comb)
```


Calculate relative fitness (divide survival by mean survival in each treatment)

```{r Calculating Individual Fitness}
# selecting individual fitness
fitness <- datTraits %>% 
  select(sampleID, treat, fracSurv) %>%
  group_by(treat) %>%
  mutate(rel.fit = fracSurv/mean(fracSurv))
head(fitness)

rel.fit.control <- fitness$rel.fit[fitness$sampleID %in% sam_control]
rel.fit.bac <- fitness$rel.fit[fitness$sampleID %in% sam_bac]
rel.fit.heat <- fitness$rel.fit[fitness$sampleID %in% sam_heat]
rel.fit.pco <- fitness$rel.fit[fitness$sampleID %in% sam_pco]
rel.fit.comb <- fitness$rel.fit[fitness$sampleID %in% sam_comb]
```

Standardize expression to z-scores

```{r}
z.score_control <- as.matrix(vsd.control)
Mean_Y = rowMeans(z.score_control,na.rm=T)
VY = apply(z.score_control,1,var,na.rm=T)
z.score_control = sweep(z.score_control,1,Mean_Y,'-')
z.score_control = sweep(z.score_control,1,sqrt(VY),'/')
z.score_control

z.score_bac <- as.matrix(vsd.bac)
Mean_Y = rowMeans(z.score_bac,na.rm=T)
VY = apply(z.score_bac,1,var,na.rm=T)
z.score_bac = sweep(z.score_bac,1,Mean_Y,'-')
z.score_bac = sweep(z.score_bac,1,sqrt(VY),'/')
z.score_bac

z.score_heat <- as.matrix(vsd.heat)
Mean_Y = rowMeans(z.score_heat,na.rm=T)
VY = apply(z.score_heat,1,var,na.rm=T)
z.score_heat = sweep(z.score_heat,1,Mean_Y,'-')
z.score_heat = sweep(z.score_heat,1,sqrt(VY),'/')
z.score_heat

z.score_pco <- as.matrix(vsd.pco)
Mean_Y = rowMeans(z.score_pco,na.rm=T)
VY = apply(z.score_pco,1,var,na.rm=T)
z.score_pco = sweep(z.score_pco,1,Mean_Y,'-')
z.score_pco = sweep(z.score_pco,1,sqrt(VY),'/')
z.score_pco

z.score_comb <- as.matrix(vsd.comb)
Mean_Y = rowMeans(z.score_comb,na.rm=T)
VY = apply(z.score_comb,1,var,na.rm=T)
z.score_comb = sweep(z.score_comb,1,Mean_Y,'-')
z.score_comb = sweep(z.score_comb,1,sqrt(VY),'/')
z.score_comb
```

Calculate selection coefficients

```{r control}
pvalue.con <- c()
slope.con <- c()

for(i in 1:dim(z.score_control)[1]){
   reg <- lm(rel.fit.control ~ z.score_control[i, ])
   slope.con[i] <- summary(reg)$coefficients[2,1]
   pvalue.con[i] <- coef(summary(reg))[, "Pr(>|t|)"][2]
}

results.control <- cbind(slope.con, pvalue.con)
rownames(results.control) <- rownames(z.score_control)
head(results.control)
```

```{r bac}
pvalue.bac <- c()
slope.bac <- c()

for(i in 1:dim(z.score_bac)[1]){
   reg <- lm(rel.fit.bac ~ z.score_bac[i, ])
   slope.bac[i] <- summary(reg)$coefficients[2,1]
   pvalue.bac[i] <- coef(summary(reg))[, "Pr(>|t|)"][2]
}

results.bac <- cbind(slope.bac, pvalue.bac)
rownames(results.bac) <- rownames(z.score_bac)
head(results.bac)
```

```{r heat}
pvalue.heat <- c()
slope.heat <- c()

for(i in 1:dim(z.score_heat)[1]){
   reg <- lm(rel.fit.heat ~ z.score_heat[i, ])
   slope.heat[i] <- summary(reg)$coefficients[2,1]
   pvalue.heat[i] <- coef(summary(reg))[, "Pr(>|t|)"][2]
}

results.heat <- cbind(slope.heat, pvalue.heat)
rownames(results.heat) <- rownames(z.score_heat)
head(results.heat)
```

```{r pco regression}
pvalue.pco <- c()
slope.pco <- c()

for(i in 1:dim(z.score_pco)[1]){
   reg <- lm(rel.fit.pco ~ z.score_pco[i, ])
   slope.pco[i] <- summary(reg)$coefficients[2,1]
   pvalue.pco[i] <- coef(summary(reg))[, "Pr(>|t|)"][2]
}

results.pco <- cbind(slope.pco, pvalue.pco)
rownames(results.pco) <- rownames(z.score_pco)
head(results.pco)
```

```{r combined combined}
pvalue.comb <- c()
slope.comb <- c()

for(i in 1:dim(z.score_comb)[1]){
   reg <- lm(rel.fit.comb ~ z.score_comb[i, ])
   slope.comb[i] <- summary(reg)$coefficients[2,1]
   pvalue.comb[i] <- coef(summary(reg))[, "Pr(>|t|)"][2]
}

results.comb <- cbind(slope.comb, pvalue.comb)
rownames(results.comb) <- rownames(z.score_comb)
head(results.comb)
```

Combined regression results with DE results

```{r}
results.allTreats <- cbind(results.control, results.bac, results.heat, results.pco, results.comb)
head(results.allTreats)

seqRes <- vsdpvals %>% column_to_rownames("X") %>%
  select_if(grepl("LFC|padj",names(.)))
head(seqRes)

coef.de <- merge(results.allTreats, seqRes, by=0)
row.names(coef.de) <- coef.de$Row.names
coef.de$Row.names <- NULL
head(coef.de)
```

```{r}
alpha <- 0.05
violin.bac <- coef.de %>% filter(padj.b<alpha) %>%
  mutate("direction" = ifelse(LFC.b>0,"up","down")) %>%
  select(slope.bac, direction) %>%
  ggplot(aes(x=direction,y=slope.bac))+
  geom_violin(aes(fill=direction))+
  geom_boxplot(width=0.1, color="grey", alpha=0.2) +
  scale_fill_manual(values=c("darkcyan","darkorange"))+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+
  theme_classic()

violin.heat <- coef.de %>% filter(padj.h<alpha) %>%
  mutate("direction" = ifelse(LFC.h>0,"up","down")) %>%
  select(slope.heat, direction) %>%
  ggplot(aes(x=direction,y=slope.heat))+
  geom_violin(aes(fill=direction))+
  geom_boxplot(width=0.1, color="grey", alpha=0.2) +
  scale_fill_manual(values=c("darkcyan","darkorange"))+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+
  theme_classic()

violin.pco <- coef.de %>% filter(padj.p<alpha) %>%
  mutate("direction" = ifelse(LFC.p>0,"up","down")) %>%
  select(slope.pco, direction) %>%
  ggplot(aes(x=direction,y=slope.pco))+
  geom_violin(aes(fill=direction))+
  geom_boxplot(width=0.1, color="grey", alpha=0.2) +
  scale_fill_manual(values=c("darkcyan","darkorange"))+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+
  theme_classic()

violin.comb <- coef.de %>% filter(padj.a<alpha) %>%
  mutate("direction" = ifelse(LFC.a>0,"up","down")) %>%
  select(slope.comb, direction) %>%
  ggplot(aes(x=direction,y=slope.comb))+
  geom_violin(aes(fill=direction))+
  geom_boxplot(width=0.1, color="grey", alpha=0.2) +
  scale_fill_manual(values=c("darkcyan","darkorange"))+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+
  theme_classic()
```
