---
title: "WGCNA for Acropora millepora Multiple Stressors"
author: "Rachel Wright"
date: "6/14/2021"
output: pdf_document
---

```{r Load Packages, echo = F}
library(tidyverse) # for plotting and data wrangling
library(DESeq2) # to variance stablize data accounting for treatment for WGCNA
library(WGCNA) # for weighted gene coexpression network analysis
library(flashClust)
library(limma) # to remove batch effects
options(stringsAsFactors=FALSE)
allowWGCNAThreads()
```

```{r Session Info}
sessionInfo()
```

```{r Load Data Files, include = F}
load("../ddsFilt.Rdata")
head(countFilt) # genes have been pre-filtered for genes with a mean count > 3
```

Create the DESeq2 object with filtered counts

```{r Create DESeq object with filtered counts}
ddsFilt <- DESeqDataSetFromMatrix(
  countData = countFilt,
  colData = conds,
  design = ~ treat + genet)
```

Perform variance stabilizing transformation with blind = FALSE for WGCNA

```{r Normalizing Genes for WGCNA}
vsd <- vst(ddsFilt, blind = FALSE) # this may take a few minutes
assay(vsd) <- limma::removeBatchEffect(assay(vsd), vsd$treat)
datExpr <- t(assay(vsd)) # transform the matrix, because WGCNA expects genes as columns and samples as rows
dim(datExpr)
# look at all of the corners to make sure the data file looks OK
datExpr[1:3,1:2]
datExpr[1:3,(ncol(datExpr)-1):ncol(datExpr)]
datExpr[(nrow(datExpr)-2):nrow(datExpr),(ncol(datExpr)-1):ncol(datExpr)]
datExpr[(nrow(datExpr)-2):nrow(datExpr),1:2]
```

Prepare trait data for WGCNA

```{r Load Trait Data}
load("../../allData.Rdata")

# make sample IDs match the expression data
datTraits <- d %>% mutate(tankID = paste("t",tank, sep=""),
                  genetTreatID = paste("g",geno,sep=""), 
                  sampleID = paste(tankID, genetTreatID, sep="_")) %>%
  select(sampleID, reef, geno, oldgeno,tank, 
         treat,bacYN, heatYN, pcoYN,
         fracSurv, growth.log, calc.log, 
         color.log, chla.log, chlc2.log,
         carb.log, prot.log, oxy.log,
         cat.log, chromo.log, po.log)
```

Need to add the "a" and "b" that indicates biological replicates (accidental clones) in the expression dataset to the trait dataset
The non-clone samples are good that don't have "NA" in the old geno are fine, just add the "a" to the sample ID

```{r fix the sample names: none clones with correct "old genos"}
datTraits <-datTraits %>% mutate(rep = rep("a",nrow(datTraits)))
datTraits$rep <- ifelse(datTraits$oldgeno=="12", "b", "a")
datTraits$rep <- ifelse(datTraits$oldgeno=="32", "b", "a")
datTraits$rep <- ifelse(datTraits$oldgeno=="20", "b", "a")

clones <- c("60", "61", "62")

goodOld.noClone <- datTraits %>% filter(!is.na(oldgeno)) %>%
  filter(!geno %in% clones) %>%
  mutate(sampleID = paste(sampleID,"a",sep="")) %>%
  select(-rep)
```

Many of the non-clone samples have "NAs" for old geno- replace them with the correct "old geno" information and add the "a" to sample ID


```{r fix non-clones with NA for old geno}
naOld.noClone <- datTraits %>% filter(is.na(oldgeno)) %>% 
  filter(!geno %in% clones) %>%
  mutate(oldgeno = geno,
         sampleID = paste(sampleID,"a",sep="")) %>%
  select(-rep)
```

Some of the clones have correct old genos- fix the sample name accordingly

```{r fix clones with correct old genos}
goodOld.clone <- datTraits %>% filter(!is.na(oldgeno)) %>%
  filter(geno %in% clones)
levels(as.factor((goodOld.clone$oldgeno)))

oldGeno_repB <- c("12", "32", "20")

goodOld.clone$rep <- ifelse(goodOld.clone$oldgeno %in% oldGeno_repB, "b", "a")
goodOld.clone <- goodOld.clone %>%
  mutate(sampleID = paste(sampleID,rep,sep="")) %>%
  select(-rep)
```

Some of the clones have "NA" for their "old geno"
We need to fix it manually by figuring out which "old geno" in that tank is already accounted for

```{r fix bad sample names}
naOld.clone <- datTraits %>% filter(is.na(oldgeno)) %>%
  filter(geno %in% clones)

naOld.clone$sampleID
# "t34_g60" "t34_g60"  # both are NA - can't be fixed
# "t34_g62" "t34_g62" # both are NA - can't be fixed
# "t34_g61" "t34_g61" # both are NA - can't be fixed

datTraits %>% filter(sampleID == "t18_g60") # missing oldgeno must be 11
naOld.clone[naOld.clone$sampleID=="t18_g60",4] <- "11"

datTraits %>% filter(sampleID == "t25_g61") # missing must be 32
naOld.clone[naOld.clone$sampleID=="t25_g61",4] <- "32"

datTraits %>% filter(sampleID == "t05_g62") # missing must be 18
naOld.clone[naOld.clone$sampleID=="t05_g62",4] <- "18"

datTraits %>% filter(sampleID == "t03_g62") # missing must be 18
naOld.clone[naOld.clone$sampleID=="t03_g62",4] <- "18"

oldGeno_repB <- c("12", "32", "20")
naOld.clone$rep <- ifelse(naOld.clone$oldgeno %in% oldGeno_repB, "b", "a")

naOld.clone <- naOld.clone %>% filter(!is.na(oldgeno)) %>% 
  mutate(sampleID = paste(sampleID,rep,sep="")) %>%
  select(-rep)
```

Now put all of the files back together
This file should be six rows shorter because we got rid of three pairs of clones that couldn't be identified confidently

```{r make big traits file}
datTraitsFix <- rbind(goodOld.clone,goodOld.noClone, naOld.clone, naOld.noClone)
nrow(datTraits)-nrow(datTraitsFix)

# look at the corners to make sure everything looks OK
datTraitsFix[1:3,1:2]
datTraitsFix[1:3,(ncol(datTraitsFix)-1):ncol(datTraitsFix)]
datTraitsFix[(nrow(datTraitsFix)-2):nrow(datTraitsFix),(ncol(datTraitsFix)-1):ncol(datTraitsFix)]
datTraitsFix[(nrow(datTraitsFix)-2):nrow(datTraitsFix),1:2]

datTraits <- datTraitsFix
```

Did we match the same samples in the expression and trait data?

```{r making sure file names match}
expressionSamples <- row.names(datExpr)
traitSamples <- c(datTraits$sampleID)

table(expressionSamples %in% traitSamples)
```

Subset the traits file for only samples that we sequenced

```{r subset traits for expression samples}
datTraitsSequenced <- datTraits %>%
  filter(sampleID %in% expressionSamples) %>% # filter for only samples that are among the sequence files
  group_by(sampleID) %>% # filter for duplicate samples (there is one duplicate and we don't know which was sequenced so toss them both)
  filter(n()==1) # replace the "==" with ">" to see duplicates
dim(datTraitsSequenced)
```

Remove the duplicate from the expression file
Make sure the order of sample names matches in both expression and data files

```{r fixing sample names}
datExpr.NoDups <- datExpr %>%
  as.data.frame() %>%
  rownames_to_column("sampleID") %>%
  filter(!sampleID=="t05_g53a") %>%
  column_to_rownames("sampleID")
# Do the sample names match exactly (including order)?
table(row.names(datExpr.NoDups) == datTraitsSequenced$sampleID) #NO!

# Fix the sample order
datTraitsSequenced.Ordered <- datTraitsSequenced[match(row.names(datExpr.NoDups), datTraitsSequenced$sampleID),]

# Do they match now?
table(row.names(datExpr.NoDups) == datTraitsSequenced.Ordered$sampleID) # YES!

datExpr <- datExpr.NoDups
datTraits <- datTraitsSequenced.Ordered
```

AHHHHH data wrangling finally done?
Save and start WGCNA

```{r save and load spot}
save(vsd, datExpr, d, datTraits, file="wgcna_start.RData")
load("wgcna_start.RData")
```


```{r Look for Sample Outliers}
gsg=goodSamplesGenes(datExpr, verbose = 3)
gsg$allOK #If the last statement returns TRUE, all genes have passed the cuts

#-----Sample dendrogram and traits
A=adjacency(t(datExpr),type="signed")

#-----Calculate whole network connectivity
k=as.numeric(apply(A,2,sum))-1

#-----Standardized connectivity
Z.k=scale(k)
thresholdZ.k=-2.5 
outlierColor=ifelse(Z.k<thresholdZ.k,"red","black")
sampleTree = flashClust(as.dist(1-A), method = "average")

#-----Convert traits to colors. Here I'm using the treatment
traitColors <- datTraits$treat
traitColors <- traitColors %>% str_replace(c("b$"), "yellow") %>% 
  str_replace("a$", "orange") %>%
  str_replace("p$", "blue") %>%
  str_replace("c$", "black") %>%
  str_replace("h$", "red")
traitColors
datColors=data.frame(outlier=outlierColor,traitColors)

#-----Plot the sample dendrogram
plotDendroAndColors(sampleTree,groupLabels=names(datColors),
                    colors=datColors,main="Sample dendrogram and trait heatmap")

#-----Remove outlying samples 
remove.samples= Z.k<thresholdZ.k | is.na(Z.k)
datExpr=datExpr[!remove.samples,]
datTraits=datTraits[!remove.samples,]
A=adjacency(t(datExpr),type="distance")
k=as.numeric(apply(A,2,sum))-1
Z.k=scale(k)

#------Double check to make sure the new files still match
table(row.names(datExpr) == datTraits$sampleID)
```

```{r save and load}
save(datExpr, datTraits, file="SamplesAndTraits.RData")
load("SamplesAndTraits.RData")
```

# Pick the soft threshold
Trim weak correlations
Find correlation power R^N where SFT.R.sq > 0.9

```{r Pick Soft Threshold}
sft <- pickSoftThreshold(datExpr, verbose=5)

# Plot the results:
powers = c(c(1:10), seq(from = 12, to=20, by=2))
sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.90,col="red")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
```

Create the adjacency matrix
This uses a signed network to create modules of either up- or down-regulated genes

```{r Create Signed Adjacency Matrix}
adjacency <- adjacency(datExpr,
                       power = 3, # choose this value from the soft-threshold plots
                       corFnc = "bicor", # correlation function
                       type = "signed")
```

Generate topological overlap matrix
This may take a few minutes

```{r TOM}
TOM <- TOMsimilarity(adjacency,
                     TOMType = "signed",
                     verbose = 0)
dissTOM <- 1-TOM
```

Make a dendrogram plotting gene clustering by TOM-based dissimilarity

```{r gene cluster dendrogram}
geneTree <- flashClust(as.dist(dissTOM), method = "average") 
plot(geneTree, labels = FALSE, xlab="", sub="", main = "Gene clustering on TOM-based dissimilarity")
```

Create Modules

```{r Creating Modules}
dynamicMods <- cutreeDynamic(dendro = geneTree,
                             distM = dissTOM,
                             cutHeight = 0.99, 
                             deepSplit = 2,
                             pamRespectsDendro = FALSE,
                             minClusterSize = 30) # the minimum number of genes in a module
table(dynamicMods)
```

Add modules to the dendrogram

```{r Add modules to the dendrogram}
dynamicColors = labels2colors(dynamicMods)
table(dynamicColors)
sizeGrWindow(8,6)
plotDendroAndColors(geneTree, dynamicColors, "Dynamic Tree Cut",
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05,
main = "Gene dendrogram and module colors")
```

Calculate module eigenenes

```{r calculating module eigengenes}
MEList = moduleEigengenes(datExpr, colors = dynamicColors)
MEs = MEList$eigengenes
# Calculate dissimilarity of module eigengenes
MEDiss = 1-cor(MEs);
# Cluster module eigengenes
METree = hclust(as.dist(MEDiss), method = "average");
# Plot the result
sizeGrWindow(7, 6)
plot(METree, main = "Clustering of module eigengenes", xlab = "", sub = "")

MEDissThres = 0.15

# Plot the cut line into the dendrogram
abline(h=MEDissThres, col = "red")
```

Merge modules based on similarity

```{r merging modules}
mergedMods <- mergeCloseModules(datExpr, dynamicColors, cutHeight = 0.15, verbose = 0)
mergedColors <- mergedMods$colors
MEList <- moduleEigengenes(datExpr, colors = mergedColors)
mergedMEs <- MEList$eigengenes
```

```{r plot dendrogram}
sizeGrWindow(12, 9)
plotDendroAndColors(geneTree, cbind(dynamicColors, mergedColors),
c("Dynamic Tree Cut", "Merged dynamic"),
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05)
```

```{r module eigengenes and colors}
moduleColors <- mergedColors
colorOrder <- c("grey", standardColors(50))
moduleLabels <- match(moduleColors, colorOrder)-1
MEs <- mergedMEs
```

Another good time to save and load

```{r save and lod}
save(MEs, moduleLabels, moduleColors, geneTree, file = "WGCNA_modules.RData")
load("WGCNA_modules.RData")
```


```{r clustering based on module eigengenes}
datME <- MEs
dissimME <- (1-t(cor(datME, method="p")))/2
hclustME <- flashClust(as.dist(dissimME), method="average" )
plot(hclustME, main="Clustering tree based on the module eigengenes")
```


```{r extract unique modules}
uniqModules <- unique(colnames(MEs))
# set in order according to ME clustering dendogram
hclustME$order
uniqModules <- uniqModules[hclustME$order]
uniqModules
# create ordered factor for downstream analysis
modules_factor <- factor(levels = uniqModules[hclustME$order], ordered = TRUE)
dt <- data.frame(uniqModules[hclustME$order])
```

# Module eigengene-trait correlations

Make your data compatible with WGCNA- which expects numerical values for all traits
For example, treatments can be "0" or "1" for the control and treatment groups

```{r format traits for WGCNA}
datTraits_forWGCNA <- datTraits %>%
  mutate("bac" = ifelse(treat=="b",1,0),
         "pco" = ifelse(treat=="p",1,0),
         "heat" = ifelse(treat=="h",1,0),
         "comb" = ifelse(treat=="a",1,0),
         "control" = ifelse(treat=="c",1,0),
         "Davies" = ifelse(reef=="Davies",1,0),
         "Rib" = ifelse(reef=="Rib",1,0),
         "Pandora" = ifelse(reef=="Pandora",1,0),
         "Esk" = ifelse(reef=="Esk",1,0)) %>%
  select(sampleID, Davies, Rib, Pandora, Esk,
         bac, pco, heat, comb, control,
         fracSurv, growth.log, calc.log, prot.log,
         color.log, chla.log, chlc2.log, carb.log, oxy.log,
         cat.log, chromo.log, po.log) %>%
  column_to_rownames("sampleID")
summary(datTraits_forWGCNA)

# make shorter version of traits
datTraits_forWGCNA <- datTraits_forWGCNA %>% select(fracSurv, growth.log, chlc2.log, carb.log)
datTraits_forWGCNA
```

Plot a sample dendrogram with all of the traits, now encoded as numbers

```{r}
sampleTree2 = hclust(dist(datExpr), method = "average")
# Convert traits to a color representation: white means low, red means high, grey means missing entry
traitColors = numbers2colors(datTraits_forWGCNA, signed = F);
# Plot the sample dendrogram and the colors underneath.
plotDendroAndColors(sampleTree2, traitColors,
                    groupLabels = names(datTraits_forWGCNA),
                    main = "Sample dendrogram and trait heatmap")
```


Module-Trait Association Heatmap

```{r make correlations}
#-----Define numbers of genes and samples
nGenes = ncol(datExpr);
nSamples = nrow(datExpr);
#-----Recalculate MEs with color labels
MEs0 = moduleEigengenes(datExpr, moduleColors)$eigengenes
MEs = orderMEs(MEs0)

#-----Correlations of genes with eigengenes
moduleGeneCor = cor(MEs,datExpr)
moduleGenePvalue = corPvalueStudent(moduleGeneCor, nSamples);

moduleTraitCor = cor(MEs, datTraits_forWGCNA, use = "p");
moduleTraitPvalue = corPvalueStudent(moduleTraitCor, nSamples);
```

Module-trait heatmap

```{r plot the heatmap}
textMatrix = paste(signif(moduleTraitCor, 2), "\n(",
                   signif(moduleTraitPvalue, 1), ")", sep = "");
dim(textMatrix) = dim(moduleTraitCor)
# Display the correlation values within a heatmap plot
labeledHeatmap(Matrix = moduleTraitCor,
               xLabels = names(datTraits_forWGCNA),
               yLabels = names(MEs),
               ySymbols = names(MEs),
               colorLabels = FALSE,
               colors = blueWhiteRed(50),
               textMatrix = textMatrix,
               setStdMargins = T,
               cex.text = 0.7,
               zlim = c(-1,1),
               main = paste("Module-trait relationships"))
```

Save and load

```{r save WGCNA results}
save(datExpr, datME, datTraits, datTraits_forWGCNA, geneTree, MEs, moduleGenePvalue, moduleColors,
     file="WGCNA_results.RData")
load("WGCNA_results.RData")
```

Make Files for Fisher of Module vs Whole Dataset for GO Analysis

```{r Fisher GO files}
datME=moduleEigengenes(datExpr,moduleColors)$eigengenes
datKME=signedKME(datExpr, datME, outputColumnName="MM.")
genes=names(datExpr)
geneInfo0 = data.frame(gene=genes,moduleColor=moduleColors)
color=data.frame(geneInfo0,datKME) #these are from your original WGCNA analysis 
levels(as.factor(color$moduleColor))

module_color <- "yellow" # replace with each module color and run the lines below

color %>% mutate("in_module_Fisher" = ifelse(moduleColor==module_color,1,0)) %>%
  select(gene, in_module_Fisher) %>% 
  write.csv(paste(module_color,"fisher.csv",sep="_"), row.names = F, quote=F)
```

Make Files for MWU of within-module kME for GO Analysis

```{r MWU based on kME GO files}
datME=moduleEigengenes(datExpr,moduleColors)$eigengenes
datKME=signedKME(datExpr, datME, outputColumnName="MM.")
genes=names(datExpr)
geneInfo0 = data.frame(gene=genes,moduleColor=moduleColors)
color=data.frame(geneInfo0,datKME) #these are from your original WGCNA analysis 
levels(as.factor(color$moduleColor))

module_color <- "turquoise" # replace with each module color and run the lines below

color %>% select(gene, moduleColor,paste("MM.",module_color,sep="")) %>%
  mutate(kME = ifelse(moduleColor==module_color, MM.turquoise, 0)) %>% # you have to manually change the color here
  select(gene, kME) %>%
  write.csv(paste(module_color,"in_mod_kME.csv",sep="_"), row.names = F, quote=F)

color %>% select(gene, paste("MM.",module_color,sep="")) %>% 
  write.csv(paste(module_color,"kME.csv",sep="_"), row.names = F, quote=F)
```

# Reaction norms of modules

```{r}
head(datTraits)
datTraits0 <- datTraits %>% column_to_rownames("sampleID") %>% 
  select(treat, fracSurv, growth.log, color.log, chlc2.log, carb.log)

traits_and_MEs <- merge(datTraits0, datME, by=0)

rxn_norm <-  traits_and_MEs %>% 
  mutate("surv_class" = as.factor(ifelse(fracSurv > 0.9, "tolerant", "susceptible")),
         "color_class" = as.factor(ifelse(color.log > 2, "tolerant", "susceptible"))) %>%
  column_to_rownames("Row.names")
summary(rxn_norm)
```

# Reaction Norm Plots

```{r rxn norm black}
ggblack <- ggplot(rxn_norm, aes(x = treat, y = MEblack)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm brown}
ggbrown <- ggplot(rxn_norm, aes(x = treat, y = MEbrown)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm blue}
ggblue <- ggplot(rxn_norm, aes(x = treat, y = MEblue)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm cyan}
ggcyan <- ggplot(rxn_norm, aes(x = treat, y = MEcyan)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm darkred}
ggdarkred <- ggplot(rxn_norm, aes(x = treat, y = MEdarkred)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm green}
gggreen <- ggplot(rxn_norm, aes(x = treat, y = MEgreen)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm greenyellow}
gggreenyellow <- ggplot(rxn_norm, aes(x = treat, y = MEgreenyellow)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm grey60}
gggrey <- ggplot(rxn_norm, aes(x = treat, y = MEgrey60)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm lightcyan}
gglightcyan <- ggplot(rxn_norm, aes(x = treat, y = MElightcyan)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm lightgreen}
gglightgreen <- ggplot(rxn_norm, aes(x = treat, y = MElightgreen)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm lightyellow}
gglightyellow <- ggplot(rxn_norm, aes(x = treat, y = MElightyellow)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm magenta}
ggmagenta <- ggplot(rxn_norm, aes(x = treat, y = MEmagenta)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm midnightblue}
ggmignightblue <- ggplot(rxn_norm, aes(x = treat, y = MEmidnightblue)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm pink}
ggpink <- ggplot(rxn_norm, aes(x = treat, y = MEpink)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm purple}
ggpurple <- ggplot(rxn_norm, aes(x = treat, y = MEpurple)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm red}
ggred <- ggplot(rxn_norm, aes(x = treat, y = MEred)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm royalblue}
ggroyalblue <- ggplot(rxn_norm, aes(x = treat, y = MEroyalblue)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm salmon}
ggsalmon <- ggplot(rxn_norm, aes(x = treat, y = MEsalmon)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm tan}
ggtan <- ggplot(rxn_norm, aes(x = treat, y = MEtan)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue"))+
  theme_bw()
```

```{r rxn norm turquoise}
ggturquoise <- ggplot(rxn_norm, aes(x = treat, y = MEturquoise)) +
  # geom_point(aes(color = surv_class), size = 2, position = position_jitter(w = 0.1, h = 0))+
  stat_summary(aes(group = surv_class), fun = mean, geom = "path") +
  stat_summary(aes(color = surv_class), fun.data = mean_cl_boot, geom = "errorbar", width = 0.1) +
  stat_summary(aes(color = surv_class), fun = mean, geom = "point", size = 4) +
  scale_color_manual(values=c("coral", "deepskyblue")) +
  theme_classic()
```

```{r}
pdf(file="fig_rxnNorm_me.pdf", width=40,height=20)
gridExtra::grid.arrange(ggblack, ggblue, ggbrown, ggcyan,
                        ggdarkred, gggreen, gggreenyellow, gggrey,
                        gglightcyan, gglightgreen, gglightyellow, ggmagenta,
                        ggmignightblue, ggpink, ggpurple, ggred, ggroyalblue,
                        ggsalmon, ggtan, ggturquoise,
                        ncol=4)
dev.off()
```

```{r}
pdf(file="fig_rxnNorm_group1.pdf", width=20,height=10)
gridExtra::grid.arrange(ggblack,ggcyan,gggreenyellow,
                        gglightgreen,ggmagenta,ggturquoise,
                        ncol=3)
dev.off()
```

```{r}
pdf(file="fig_rxnNorm_group2.pdf", width=20,height=10)
gridExtra::grid.arrange(ggblue,ggdarkred,gggreen,
                        ggpink, ggpurple,ggtan,
                        ncol=3)
dev.off()
```

```{r}
pdf(file="fig_rxnNorm_group3.pdf", width=20,height=10)
gridExtra::grid.arrange(ggbrown,ggred,ggsalmon,
                        gglightyellow,gggrey,
                        ncol=3)
dev.off()
```

```{r}
pdf(file="fig_rxnNorm_group4.pdf", width=20,height=5)
gridExtra::grid.arrange(gglightcyan,ggmignightblue,ggroyalblue,
                        ncol=3)
dev.off()
```
